Analysis for Project

### 2021-11-23 analysis/analysis.Rmd
Add model with strict parent linking

```{r models-by-grade, warning=FALSE}
#run separate models by grade groups
model4_elem <- update(model4, data=subset(acs, current_grade<="5th"))
model4_middle <- update(model4, data=subset(acs, current_grade>"5th" & 
                                        current_grade<"9th"))
model4_hs <- update(model4, data=subset(acs, current_grade>="9th"))

@@

>>>>

```{r models-by-grade, warning=FALSE, fig.height=12}
#run separate models by grade groups
model4_elem <- update(model4, data=subset(acs, current_grade<="5th"))
model4_middle <- update(model4, data=subset(acs, current_grade>"5th" & 
                                        current_grade<"9th"))
model4_hs <- update(model4, data=subset(acs, current_grade>="9th"))

@@

## Models with stricter parent linking

```{r models-parent-link, warning=FALSE, fig.height=12}
#run separate models by grade groups
model4_best_link <- update(model4, data=subset(acs, momrule==11 & poprule==11))

coef_table_best_link <- calculate_marg_means(model4_best_link, 
                                        cluster_var=subset(acs, momrule==11 &
                                                             poprule==11)$cluster)

coef_table <- coef_table_best_link %>%
  mutate(model="only direct links")
coef_table <- coef_table_mod4 %>%
  mutate(model="all links") %>%
  bind_rows(coef_table) %>%
  mutate(model=factor(model, levels=c("all links","only direct links")),
         mrace=factor(mrace, levels=c("Black/White",
                                      "Black/Latino",
                                      "Black/Asian",
                                      "Black/Indigenous",
                                      "White/Indigenous",
                                      "White/Latino",
                                      "White/Asian",
                                      "Latino/Asian",
                                      "Indigenous/Latino",
                                      "Indigenous/Asian")))
